Economic Theory of Fertility Explains Modern Natural Selection

### 2020-11-19 why-negative-selection.Rmd
add manual checks of every result. Use Anova to check for interaction effects when controlling for age.

n_in_regs <- function (var, dv = "n_children") {
  fh_subset <- famhist
  if (dv == "n_children") fh_subset %<>% filter(age_at_recruitment >= 45)
  # all PGS have the same NA pattern, so we just use one
  tbl <- table(fh_subset[
                  ! is.na(fh_subset[dv]) & ! is.na(fh_subset$whr_combined), 
                  var
                ])

@@

* Check each result with a manually done regression!
* If we weight with the GHS, and plot the means of figure 1 using this w
  weighting, most things stay the same - but the change in EA is reversed! EA
  increases over time. Could this be because the sample includes many
  relatively educated older people? If so, then mean effects are *overestimated*
  by figure 1.
* Reweight other regressions (e.g. the omnibus regression in the appendix)?
* Look at geography, esp. in siblings regressions 
  - maybe Townshend f.189? Not sure essential
* Another point is that negative selection only among poor will increase
    genetic inequality.
* When we have better definition of "partner", bring it across from the other
  project to define with_partner
  - `with_partner` is fine, but if you want to have pairs who had the same children
  you need to do more
* If you take "year of last job started" and see if it is after/before
  the first child, you can figure out whether mothers keep working.
  - better still, look at all jobs started and see if any are within e.g. 5 years of
  first child's birth
  - this could then be another way to get at income vs substitution effects. You'd
  predict negative selection effects among mothers who worked. Of course the
  choice to work is endogenous.
* double check which scores are reverse coded!

@@

```{r plot-n-partners-controlled, fig.cap = "Selection effects by number of sexual partners (median split at 3), controlling for respondent's age and age squared."}
drake::loadd(res_partners_controlled)
res_partners_controlled %<>%       
      filter(term != "(Intercept)", term != "lo_partnersTRUE") %>% 
      mutate(`N partners` = ifelse(grepl("TRUE:", term), "<= 3", "> 3"))

>>>>

n_in_regs <- function (var, dv = "n_children") {
  fh_subset <- famhist
  if (dv == "n_children") fh_subset %<>% filter(kids_ss)
  # all PGS have the same NA pattern, so we just use one
  tbl <- table(fh_subset[
                  ! is.na(fh_subset[dv]) & ! is.na(fh_subset$whr_combined), 
                  var
                ])

@@

* Limit max no. of children in regressions (use an "in_children" bool)
  - not necessary. Very few have abnormally many.
* Check each result with a manually done regression!
* Consider doing separate regressions for "any children" vs. "n children | 1 or more"
  - heckit too slow and gives crazy answers, just use plm/ols
  - some variables do look different
* If we weight with the GHS, and plot the means of figure 1 using this w
  weighting, most things stay the same - but the change in EA is reversed! EA
  increases over time. Could this be because the sample includes many
  relatively educated older people? If so, then mean effects are *overestimated*
  by figure 1.
* Reweight other regressions (e.g. the omnibus regression in the appendix)?
* Look at geography, esp. in siblings regressions 
  - maybe Townshend f.189? Not sure essential
* Another point is that negative selection only among poor will increase
    genetic inequality.
* When we have better definition of "partner", bring it across from the other
  project to define with_partner
  - `with_partner` is fine, but if you want to have pairs who had the same children
  you need to do more
* If you take "year of last job started" and see if it is after/before
  the first child, you can figure out whether mothers keep working.
  - better still, look at all jobs started and see if any are within e.g. 5 years of
  first child's birth
  - this could then be another way to get at income vs substitution effects. You'd
  predict negative selection effects among mothers who worked. Of course the
  choice to work is endogenous.
* double check which scores are reverse coded!

@@

```{r plot-n-partners-controlled, fig.cap = "Selection effects by number of sexual partners (median split at 3), controlling for respondent's age and age squared."}
drake::loadd(res_partners_controlled)
res_partners_controlled %<>%       
      mutate(`N partners` = ifelse(grepl("TRUE", term), "<= 3", "> 3"))
